Make any stupid plot you want

### 2021-01-06 draft/sections/math.tex
monoids

\begin{equation}
    \label{eq:artist}
    A: \mathcal{O}(E) \rightarrow \mathcal{O}(H)
\end{equation}

\begin{itemize}
\item $A$ is the function that converts an instance of data $\Gamma(E)$ to an instance of a visual representation $\Gamma(H)$ 
\item $E$ is a locally trivial fiber bundle over $K$ representing data space.
\item $K$ is a triangulizable space encoding the connectivity of the points in $E$
\item $H$ is a fiber bundle over $S$ representing visual space
\item $S$ is a simplacial complex encoding the visualization
\end{itemize}

@@

\subsubsection{Base space}
\begin{figure}[ht]
    \label{fig:base_space}
    \includegraphics[width=0.4\linewidth]{figures/sections/math/k_qspace.png}
\end{figure}

@@

\begin{figure}[ht]
    \label{fig:data_fiber_bundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
\end{figure}

@@

\begin{figure}[ht]
    \label{fig:simplex}
    \includegraphics{figures/sections/math/simplex.png}
    \caption{Simplices encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations. Higher order simplicies are outside the scope of this paper.}
\end{figure}

@@

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}

@@

\subsubsection{Example}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2f.png}
    \label{fig:}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_3f.png}
\end{figure}

@@

\subsubsection{{Example}}
\begin{figure}[h]
    \includegraphics[width=.4\linewidth]{figures/sections/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} in fiber $P$. The visual transformer $\nu$ is a set of functions each targeting a different $\mu$
\begin{equation}
    \label{eq:nu_expanded}
    \nu:\{\nu_{0}, \ldots, \nu_{n}\} \rightarrow \{\mu_{0}, \ldots, \mu_{n}\}
\end{equation}

@@

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \label{tab:mpl_visual_variable_fiber}
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, linecolor, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $(\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
\end{table}

\subsubsection{Visual Channels}
$\nu: \tau \mapsto \mu$ is an equivariant map such that there is a homomorphism from monoid actions on $E_{i}$ to manoid actions on $V_{i}$  
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "f"'] & V_i \arrow[d, "f"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
where the diagram commutes such that  $\nu_{i}\circ f(\tau_{i}) = f \circ \nu_{i}(\tau_{i})$. A monoid is a set $M$ with a closed associative binary operation ($\*$) and an identity element $e$.

@@

\subsubsection{Constructing Marks}
The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "Q"] \arrow[rd, "\xi^*\pi"'] & H \arrow[d, "\pi"] \\
                                                      & S                 
    \end{tikzcd}
\end{equation}
the function $Q:\xi^*V\rightarrow H$ composites points in $V$ into $\mathbb{R^7}$ tuples. The section $\mu$ is pulled over $s$

\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "Q"] & H                                           \\
                              & S \arrow[lu, "\xi^*\mu"] \arrow[u, "\rho"']
    \end{tikzcd}
\end{equation}

such that the composition $Q$ of $\mu$ is equivalent to the render $\rho(s) = Q\circ\mu(s)$. 
(In practice $\mu \approxeq \xi^*\mu$)
$Q$ is the constructor for the mark, 
one $Q$ per artist, A = sum of artists
$Q$ as there's default line, point, etc that's stretched and tweaked and whatever else by the $\mu$
visual variable + structure preserving, Q must have map that commutes such that a change in $\mu$ carries over somehow to $\rho$, functorial in its arguments - commutative diagram - into rho

Bertin describes a location on the plane as the signifying characteristic of a point, measurable length as the signifying characteristic of a line, and measurable size as the signifying characteristic of an area and that in display (pixel) space are the point, line, and area marks \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology}. For each region $s$ in the display space $H$, the mark it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$ then taking $\xi(s)$ back to a point on $k \in K$ which lies on the connected component $J \subset K$. 
\begin{equation}
\begin{tikzcd}
    H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K| \exists \Gamma \text{ s.t. } \Gamma(0)=k \text{ and }\Gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
\end{tikzcd}
\label{eq:mark}
\end{equation}
To got back to the display space $H$  from the simplacial complex $J$ of the signifier implanted in the mark, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then  $\rho(\xi^{-1}(J))$ maps it into $R^{7}$.

>>>>

\begin{equation}
    \label{eq:artist}
    A: \Gamma(E) \rightarrow \Gamma(H)
\end{equation}

\begin{itemize}
\item $A$ is the function that converts an instance of data $\Gamma(E)$ to an instance of a visual representation $\Gamma(H)$ 
\item $E$ is a locally trivial fiber bundle over $K$ representing data space.
\item $K$ is a triangulizable space encoding the connectivity of the points in $E$
\item $H$ is a fiber bundle over $S$ representing visual space
\item $S$ is a simplacial complex encoding the visualization
\item $\Gamma$ is the global space of sections
\end{itemize}

@@

\subsubsection{Base space}
\begin{figure}[H]
    \label{fig:base_space}
    \includegraphics[width=0.4\linewidth]{figures/sections/math/k_qspace.png}
\end{figure}

@@

\begin{figure}[H]
    \label{fig:data_fiber_bundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
\end{figure}

@@

\begin{figure}[H]
    \label{fig:simplex}
    \includegraphics{figures/sections/math/simplex.png}
    \caption{Simplices encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations. Higher order simplicies are outside the scope of this paper.}
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}

@@

\subsubsection{Example}
\begin{figure}[H]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2f.png}
    \label{fig:}
\end{figure}
\begin{figure}[H]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_3f.png}
\end{figure}

@@

\subsubsection{{Example}}
\begin{figure}[H]
    \includegraphics[width=.4\linewidth]{figures/sections/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} in fiber $P$. The visual transformer $\nu$ is a set of functions each targeting a different $\mu$
\begin{equation}
    \label{eq:nu_expanded}
    \{\nu_{0}, \ldots, \nu_{n}\}: \{\tau_{0}, \ldots, \tau_{n}\} \mapsto \{\mu_{0}, \ldots, \mu_{n}\}
\end{equation}

@@

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \label{tab:mpl_visual_variable_fiber}
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
\end{table}

\subsubsection{Visual Channels}
$\nu: E \rightarrow V$ is an equivariant map such that there is a homomorphism from left monoid actions on $E_{i}$ to left monoid actions on $V_{i}$ where $i$ identifies a field in the fiber.  A validly constructed $\nu$ is one where the  diagram
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "m"'] & V_i \arrow[d, "m"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
 commutes such that $\nu_i(m(E_i)) = m(\nu_i(E_i))$ where $m$ is a monoid action. $E_i$ and $V_{i}$ each contain a set of values as defined in $F$ and $P$ respectively.

\paragraph{Definition}
A monoid\cite{Monoid2021} $M$ is a set that is closed under an associative binary operator $\ast$ and has an identity element $e\in M$ such that $e\ast a= a \ast e = a$ for all $a \in M$.  A left monoid action \cite{SemigroupAction2021,ActionNLab} of $M$ is a set $X$ with an operation $\cdot$ with the monoid properties:
\begin{description}
    \item[closure] $\cdot: M\times X \rightarrow X$
    \item[associativity] $\text{for all} m,t \in M \text{and} x\in X, m\cdot(t\cdot x) = (m\ast t)\cdot x$ 
    \item[identity] $\text{for all} x\in X, e\in M,  e\cdot x = x$ 
\end{description}

@@

\subsubsection{Assembling Marks}

\begin{figure}[H]
    \includegraphics[width=0.4\linewidth]{figures/sections/math/path_of_q}
    \label{fig:q}
    \caption{change $\rho$ to input J}
\end{figure}

The assembly function $Q: \Gamma(V) \rightarrow \Gamma(H)$ composites the visual variables in $V$ into an element in $H$. Given a monoid action on a set in $V$, there should be a monoid action on the corresponding $Q(\Gamma(V))$. <why gamma?

Lets call $\Gamma(V) = X$ and $Q(\Gamma(V))$

For each region $s$ in the display space $H$, the mark  \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology} it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$ then taking $\xi(s)$ back to a point on $k \in K$ which lies on the path connected component $J \subset K$. 
\begin{equation}
    \begin{tikzcd}
        H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K| \exists \gamma \text{ s.t. } \gamma(0)=k \text{ and }\gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
    \end{tikzcd}
    \label{eq:mark}
\end{equation}
where $\gamma$ is a path where input is a point on the interval [0,1] and

To get back to the display space $H$ from $J$, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then $\rho(\xi^{-1}(J))$ maps it into $R^{7}$ such that $Q\circ\xi^*\mu(\xi^{-1}(J))$ generates a graphical mark.

%%abs: R \rightarrow R^+, 
%%f: R \rightarrow R, 
%%abs:[real->real] -> [real->real+]
%%fmap?, fmap(abs)->ufunc on all functions
%%lifting: decorator that only looks at arguments

Q goes from one to the other, could need more information than just the return values... map on global sections means I might need to know the whole section, map V to H says I only need to know points, restrict to the case where defined on the stalk..but will look at particular cases - sections to sections is most general case that is true, but can be defined V to H or or O(V) to O(H) depending on the visualization.
